Inferring the Recombinant Genealogy of a Pandemic Pathogen in Real Time

### 2025-09-05 latex/main.tex
Incorporate recombinant QC fig

\begin{figure}
    \centering
    % \includegraphics{sc2ts_methodology}
    \caption{Classification of ``robust'' and artifactual recombination events.
(A) Scatterplot of recombination events by the net number of supporting loci
for the left parent (x-axis) and for the right parent (y-axis). The shaded
regions highlight artifactual recombination events, which have fewer than four
net supporting loci on one side or both sides of the suggested breakpoint.
Colors indicate the primer scheme used for sequencing. The pie charts show
breakdowns of the recombination events by primer scheme per quadrant.
Recombination events associated with the origins of Pango Xs are labeled
(classified in Figure 2). (B) Copying patterns of an illustrative recombination
event picked from each quadrant.
}\label{fig:recombinant_qc}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{robust_vs_artificial_classification}
    \caption{Classification of ``robust'' and artifactual recombination events.
Scatterplot of recombination events by the net number of supporting loci
for the left parent (x-axis) and for the right parent (y-axis). The shaded
regions highlight artifactual recombination events, which have fewer than four
net supporting loci on one side or both sides of the suggested breakpoint.
Colors indicate the primer scheme used for sequencing. The pie charts show
breakdowns of the recombination events by primer scheme per quadrant.
Recombination events associated with the origins of Pango Xs are labeled.
}\label{fig:recombinant_qc}
\end{figure}
